Spatial Reasoning and Statistical Graphics

### 2014-10-22 Paper/Draft1/TestingVisualAptitude.Rnw
Showing history of ETS Kit tests

Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} from which parts of this test are drawn.

\comment{could we also refer to the fact that these tests have been long established (maybe with references to earlier tests or updates?) \textit{Yes, definitely. I'll pull up some references for that too...}}
The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied (including an extensive meta-analysis by \citet{voyer1995magnitude} of the spatial tests we are using in this study) and comparison data are available from the validation of these factors \citep{schaie1998longitudinal,hampson1990variations,mayer1994whom} and previous versions of the kit \citep{educational1963kit}.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?\\\textit{I was working on it yesterday along with trying to validate the general idea that reading graphics requires certain spatial abilities. It's definitely a work in progress. I haven't seen that book before, but I'm not at all surprised it exists.}}

>>>>

Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} from which parts of this test are drawn. The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied (including an extensive meta-analysis by \citet{voyer1995magnitude} of the spatial tests we are using in this study) and comparison data are available from the validation of these factors \citep{schaie1998longitudinal,hampson1990variations,mayer1994whom} and previous versions of the kit \citep{educational1963kit}.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?\\\textit{I was working on it yesterday along with trying to validate the general idea that reading graphics requires certain spatial abilities. It's definitely a work in progress. I haven't seen that book before, but I'm not at all surprised it exists.}}
